Spirals launched by a planet in a shadowed disk

### 2024-04-14 src/tex/ms.tex
Finish spiral morphology

\begin{figure}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/zeta_wide.pdf}
        \script{plot_zeta_wide.py}
        \caption{
            Same as Figure \ref{fig:zeta_narrow} but for the wide case. Note that the variations in the inset are much more continuous than in the
            narrow case, and have a much larger amplitude.
        }
        \label{fig:zeta_wide}
    \end{center}
\end{figure}

The shape of a spiral can be parameterized by its initial condition $\phi(r_0)$ and by its pitch angle $\zeta$. Pitch angle
is defined as
\begin{equation}
    \cot \zeta = \frac{d\phi}{d \ln r}
\end{equation}

according to \citet{zhu2022}. We use a central difference scheme to take the numerical derivative of $\phi_{\rm peak}$ with respect to $\ln r$.

>>>>

\begin{figure}
    \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/zeta_wide.pdf}
        \script{plot_zeta_wide.py}
        \caption{
            Same as Figure \ref{fig:zeta_narrow} but for the wide case. Note that the variations in the inset are much more continuous than in the
            narrow case, and have a much larger amplitude. Variations also evident interior to the planet, but the features are not as long-lived
            as those outside.
        }
        \label{fig:zeta_wide}
    \end{center}
\end{figure}

The shape of a spiral can be parameterized by its initial condition $\phi(r_0)$ and by its pitch angle $\zeta$. Pitch angle
is defined as
\begin{equation}
    \cot \zeta = \frac{d\phi}{d \ln r}
    \label{zeta_def}
\end{equation}

according to \citet{zhu2022}. We use a central difference scheme to take the numerical derivative of $\phi_{\rm peak}$ with respect to $\ln r$.
\citet{zhu2022} also provides an analytic solution in the limit that the wave has propagated far enough away from the planet:

\begin{equation}
    \zeta = \arctan |(\Omega_{\rm pat} - \Omega)r/c_{\rm s}|
\end{equation}

where $\Omega$ is the local Keplerian frequency and $\Omega_{\rm pat}$ is the Keplerian frequency at the
radius from which the spiral is launched. As we are only considering circular orbits we see that 
$\Omega_{\rm pat} = \Omega(r=1)$ and the pitch angle reduces to

\begin{equation}
    \cot \zeta = |(1-r^{-3/2}) r/c_{\rm s}|
    \label{eq:zeta_omega}
\end{equation}

We plot this analytic case against our numerical results in Figures \ref{fig:zeta_narrow} \& \ref{fig:zeta_wide}. While the simulation with
no shadow matches this solution very well we see that both shadowed cases display oscillations -- particularly far outside the planet's orbit.
We can see that if $r$ is held constant then $\zeta$ is purely a function of the sounds speed $c_{\rm s}$. We can set
Equations \ref{eq:zeta_def} \& \ref{eq:zeta_omega} equal to each other to find

\begin{equation}
    \frac{d\phi}{d r} = \frac{1-r^{-3/2}}{c_{\rm s}}
\end{equation}

where we have removed the log from the differential and divided out the additional factor of $r$. We can separate the differential to see
\begin{equation}
    \int_{\phi_p}^{\phi_f} c_{\rm s} d \phi = \int_{1}^{r_f} (1-r^{-3/2}) d r
    \label{eq:analytic_shadow}
\end{equation}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/spiral_shape_analytic.pdf}
    \caption{
        Analytic spiral curves for a variety of situations. Here we consider both the narrow and wide cases for multiple values of $h$.
        The $h=0.9$ case which we simulate numerically very nearly matches the shadowless case, shown in black. In order to get
        variations similar to those seen in our simulations we have to set $h$ to be much less than 1.
    }
    \label{fig:analytic_spiral}
    \script{plot_sound_speed_analytic.py}
\end{figure}

$c_{\rm s}(\phi)$ is non-trivial to integrate by hand, but can be done very easily numerically. We solve Equation \ref{eq:analytic_shadow}
using the Newton-Raphson method to find $\phi_f$ for a given $r_f$. Figure \ref{fig:analytic_spiral} shows that the sound speed variations
present in our simulations are insufficient to produce the spiral shapes we observe. Therefore, there must be some secondary effect not accounted for
in the analytic approximation that is causing these variations. Likely, it is some interaction between the planet's spiral and spirals caused by the
shadow; we explore this in Section \ref{subsec:spiral_shadow}.

\subsection{Spirals launched by the shadow}
\label{subsec:spiral_shadow}
